---
title: "Bioinformatics tools & workflows on BioCommons partner infrastructures"
---

<style type="text/css">
.main-container {
  max-width: 1500px;
  margin-left: auto;
  margin-right: auto;
}
</style>

This page details tool request mechanisms and a list of tools and workflows installed across several of the [BioCommons infrastructure partner systems](./1_compute_systems.html). Tool status on other partner infrastructures will be added over time.

-----

-----

```{r setup, include=FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(yaml)
library(kableExtra)
#lubridate included to allow for automated provision of date for tool list update
#see https://r4ds.had.co.nz/dates-and-times.html
library(lubridate)
library(DT)

#see https://stackoverflow.com/questions/13548266/define-all-functions-in-one-r-file-call-them-from-another-r-file-how-if-pos
source("functions.R")
```

<a name="tool_request"></a>

# Requesting tool installations

Tool installs can be requested for the infrastructures listed in the table:

<font size="-1.5">
```{r}

tool_request <- tibble(
  Infrastructure = c("[Galaxy Australia](https://usegalaxy.org.au/)",
                     "[NCI](https://nci.org.au/)",
                     "[Pawsey](https://pawsey.org.au/)",
                     "[QRIScloud](https://www.qriscloud.org.au/) / [UQ-RCC](https://rcc.uq.edu.au/)"),
  Process = c("Complete a [tool install request](https://request.usegalaxy.org.au/)",
              "[Contact NCI](https://opus.nci.org.au/display/Help/5.+Software+Applications)",
              "Visit the [Helpdesk Portal](https://support.pawsey.org.au/portal/servicedesk/customer/portal) or email: [help@pawsey.org.au](help@pawsey.org.au) with your request",
              "Complete a [tool install request](https://docs.google.com/forms/d/e/1FAIpQLSefKCBkZbTQ-dUyU-pd4ZypkA-TA5GiMgpsJ2slWmD-B6elEg/viewform)"
              )
    )

#see https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
tool_request %>%
  kbl(escape = FALSE, align = "l") %>%
  kable_styling(bootstrap_options = c("striped"))

```
</font>

### FAQ: can I get a HPC allocation through the BioCommons?

Allocation of computational resources to individual researchers on partner HPC and cloud infrastructures is through the usual channels offered via each partner (see instructions for each by following these links: [NCI](https://nci.org.au/users/how-access-nci), [Pawsey](https://support.pawsey.org.au/documentation/display/US/Getting+Access), [QCIF](https://www.qcif.edu.au/services/computing/), [ARDC-Nectar](http://cloud.nectar.org.au/start-now/)). The [BioCommons BioCloud](https://www.biocommons.org.au/biocloud) activity is working with these partners to examine ways to make it easier for life science researchers to receive HPC and HTC allocations.

Note that access to computational resources via the [Galaxy Australia](https://usegalaxy.org.au/) hosted web platform is unlimited for Australian researchers thanks to our computational partners (ARDC-Nectar Cloud, University of Queensland, QCIF, University of Melbourne and Pawsey) who underpin the Galaxy Australia service.  

```{r}
######################
###load matrix data###
######################
data <- read_matrix("../../external_GitHub_inputs/Matrix of Availability of Bioinformatics Tools across BioCommons - deployment version - Bioinformatics Software Availability.tsv")

######################
###load galaxy data###
######################
galaxy <- parse_GA_yaml(list.files("../../external_GitHub_inputs/usegalaxy.org.au/", full.names = TRUE))

#########################
###load QRIScloud data###
#########################
qris <- read_qris("../../external_GitHub_inputs/qriscloud.txt") %>%
  rename(`QRIScloud / UQ-RCC (Flashlite, Awoonga, Tinaroo)` = qris_cloud) %>%
  #see https://community.rstudio.com/t/which-tidyverse-is-the-equivalent-to-search-replace-from-spreadsheets/3548/7
  mutate_if(is.character, str_replace_all, pattern = 'genomeanalysistk', replacement = 'gatk') %>%
  mutate_if(is.character, str_replace_all, pattern = '^pacbio$', replacement = 'smrtlink') %>%
  mutate_if(is.character, str_replace_all, pattern = '^soapdenovo$', replacement = 'soapdenovo2')

####################  
###load Gadi data###
####################
gadi <- read_gadi("../../external_GitHub_inputs/gadi.csv") %>%
  rename(`NCI (Gadi)` = version)

######################
###load Pawsey data###
######################
zeus <- read_hpc("../../external_GitHub_inputs/zeus.txt") %>%
  rename(`Pawsey (Zeus)` = version) %>%
  #see https://community.rstudio.com/t/which-tidyverse-is-the-equivalent-to-search-replace-from-spreadsheets/3548/7
  mutate_if(is.character, str_replace_all, pattern = 'wgs', replacement = 'celera') %>%
  mutate_if(is.character, str_replace_all, pattern = 'trinityrnaseq', replacement = 'trinity')

magnus <- read_hpc("../../external_GitHub_inputs/magnus.txt") %>%
  rename(`Pawsey (Magnus)` = version)

#################################
###join and process tool lists###
#################################
COMPLETE <- join_and_process_tools(matrix_data = data, 
                                   gadi_data  = gadi, 
                                   zeus_data = zeus, 
                                   magnus_data = magnus, 
                                   qris_data = qris, 
                                   galaxy_data = galaxy)

###other links
#see https://stackoverflow.com/a/56683740
#see https://stackoverflow.com/questions/43696227/mutate-with-case-when-and-contains

```

-----

-----

<a name="tool_information"></a>

# Tool information {.tabset .tabset-pills}

## Tool install status and version availability

<font size="-1.5">
```{r}

installs <- COMPLETE %>%
  #see https://tidyr.tidyverse.org/reference/replace_na.html
  replace_na(list(`Galaxy Australia` = "",
                  `Pawsey (Zeus)` = "",
                  `Pawsey (Magnus)` = "",
                  `QRIScloud / UQ-RCC (Flashlite, Awoonga, Tinaroo)` = "",
                  `NCI (Gadi)` = "",
                  `Primary purpose (EDAM, if available)` = ""
                  )) %>%
  rename(`Tool identifier (module name / bio.tools ID / placeholder)` = toolID) %>%
  select(`Tool / workflow name`,
         `Tool identifier (module name / bio.tools ID / placeholder)`,
         `Primary purpose (EDAM, if available)`,
         `Galaxy Australia`, 
         `NCI (Gadi)`, 
         `Pawsey (Zeus)`, 
         `Pawsey (Magnus)`, 
         `QRIScloud / UQ-RCC (Flashlite, Awoonga, Tinaroo)`
         )

#see https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
#kable(installs, format = "pipe", align = "c")

#https://bookdown.org/yihui/rmarkdown/interactive-documents.html
#https://rstudio.github.io/DT/
datatable(installs, options = list(pageLength = 20), class = 'cell-border stripe', style = 'bootstrap', escape = FALSE)

```
</font>

**Note:** 

- Table last updated ```r today()```.
- Software documentation is linked from the *Tool / workflow name* in the first column.
- The *Tool identifier* column contains an identifier for the tool / workflow: typically either the module name (used for matching to HPC lists), a bio.tools ID, or a  placeholder value.
- For tools which are not currently installed on [Galaxy Australia](https://usegalaxy.org.au/), but which are available [in the Galaxy app store (aka toolshed)](https://toolshed.g2.bx.psu.edu/), the *Available in Galaxy toolshed* column launches a toolshed search using the link label as the search term.
- The list currently includes some tools that are not used for bioinformatics.
- The source material for the table is currently manually curated, and while we endeavour to keep the information as current as possible, there is a natural limit to the volume of information maintained here. Production of this information will be automated during 2021, and tools that are not relevant for bioinformatics analyses removed.

-----

-----

## Tool information

<font size="-1.5">
```{r}
info <- COMPLETE %>%
  #see https://tidyr.tidyverse.org/reference/replace_na.html
  replace_na(list(`bio.tools` = "",
                  `BioContainers` = "",
                  `Available in Galaxy toolshed` = "",
                  `Primary purpose (EDAM, if available)` = "")) %>%
  rename(`Tool identifier (module name / bio.tools ID / placeholder)` = toolID) %>%
  select(`Tool / workflow name`,
         `Tool identifier (module name / bio.tools ID / placeholder)`,
         `Primary purpose (EDAM, if available)`,
         `Available in Galaxy toolshed`,
         `bio.tools`, 
         `BioContainers`)

#https://bookdown.org/yihui/rmarkdown/interactive-documents.html
#https://rstudio.github.io/DT/
datatable(info, class = 'cell-border stripe', escape = FALSE)

```
</font>

**Note:** 

- Table last updated ```r today()```.
- Software documentation is linked from the *Tool / workflow name* in the first column.
- The *Tool identifier* column contains an identifier for the tool / workflow: typically either the module name (used for matching to HPC lists), a bio.tools ID, or a  placeholder value.
- The *Primary purpose* column categorises the tools by purpose, using an [EDAM](https://github.com/edamontology/edamontology) *topic* where possible.
- More information about a tool can be found by following the link in the [bio.tools](https://bio.tools/) column.
- When a tool has been containerised to allow for easier installation on any compute infrastructure, a link to the containerised software that can be downloaded  is shown in the [BioContainers](https://biocontainers.pro/#/) column.
- The list currently includes some tools that are not used for bioinformatics.
- The source material for the table is currently manually curated, and while we endeavour to keep the information as current as possible, there is a natural limit to the volume of information maintained here. Production of this information will be automated during 2021, and tools that are not relevant for bioinformatics analyses removed.

-----

-----

# How were the tools and workflows selected?

The tool list here includes those that have been identified through [BioCommons Community consultations](https://www.biocommons.org.au/get-involved) and other engagements, as well as through matching to the tool sets installed across the various BioCommons partner compute infrastructures. The list is not intended to be exhaustive: i.e. it does not contain *ALL* bioinformatics tools.

-----

-----

# How was the list generated?

RStudio (see session info at the bottom of this page) was used for processing. 

The broad steps are described here:

<font size="-1.5">

1. The manually curated tool list and separate tool lists provided by the BioCommons partner infrastructures were parsed (Galaxy Australia, NCI, Pawsey and QRISCloud - RCC). 
2. The complete set of tool lists were joined using the ```toolID``` as a key, and 
3. Links were embedded, where available, to the original documentation URLs (homepage or GitHub repository, for example) as well as the registry entries on bio.tools and BioContainers. 
4. Galaxy wrapping often entails that tool suites are separated into their individual tool components. As such, if a Galaxy tool was matched to the manually curated tool list, a tool shed search link was embedded in the ```Available in Galaxy toolshed``` column. This allows a user to search for the tool using a relevant search term (e.g. vcftools) to identify all the component tools available in the toolshed.

</font>

-----

-----

## Session information

```{r}
sessionInfo()
```

-----

-----

```{r echo = FALSE, message = FALSE}
#see https://bookdown.org/yihui/rmarkdown-cookbook/write-bib.html
library(knitr)
write_bib(c(.packages()), "./outputs/tools_packages.bib")
```
