---
title: "Featured tools & workflows"
---

<style type="text/css">
.main-container {
  max-width: 1500px;
  margin-left: auto;
  margin-right: auto;
}
</style>

A list of Australian BioCommons documentation repositories is provided below. The tools and workflows documented were initially identified through consultations with the [BioCommons Communities of practice](https://www.biocommons.org.au/get-involved), as well as active [Bioplatforms Australia Framework Initiatives](https://bioplatforms.com/projects/).

-----

-----

# Tools and workflows

```{r setup, include = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(kableExtra)
```

<font size="-1.5">
```{r}
biocommons <- read_tsv("../../external_GitHub_inputs/complete_processed_tool_matrix.tsv") %>%
  filter(grepl("github", `BioCommons Documentation`)) %>%
  #see https://tidyr.tidyverse.org/reference/replace_na.html
  replace_na(list(`bio.tools` = "",
                  `BioContainers` = "",
                  `BioCommons Documentation` = "",
                  `Primary purpose (EDAM, if available)` = "")) %>%
  select(`Tool / workflow name`, `Primary purpose (EDAM, if available)`, `BioCommons Documentation`, `bio.tools`, `BioContainers`)

kable(biocommons, format = "pipe", align = "c")
```
</font>


**Please note**:

- Software documentation is linked from the *Tool / workflow name* in the first column.
- More information about a tool can be found by following the link in the [bio.tools](https://bio.tools/) column.
- When a tool has been containerised to for easier installation on any compute infrastructure, a link to the containerised software is shown in the [BioContainers](https://biocontainers.pro/#/) column.

-----

-----

# What do each of the listed tool and workflow repositories contain?

Each repository is structured using our [documentation guidelines](https://github.com/AustralianBioCommons/doc_guidelines/releases) (for [Tools](https://github.com/AustralianBioCommons/doc_guidelines/blob/master/docs/tools.md), [Workflows](https://github.com/AustralianBioCommons/doc_guidelines/blob/master/docs/workflows.md) or [Infrastructure](https://github.com/AustralianBioCommons/doc_guidelines/blob/master/docs/infrastructure_optimisation.md)) that have been developed through engagement with community bioinformaticians. Real-world use cases informed iterative development to produce a first version of these guidelines.

We will continue to work together with the community to build a fit-for-purpose and standardised approach for presenting tool and workflow documentation which contains information specific to Australian HPC and Cloud infrastructure. These guidelines and the documentation therein will be developed in line with community requirements, and will align closely to global efforts (e.g. that being undertaken by the [ELIXIR tools platform](https://elixir-europe.org/platforms/tools)).


```{r echo = FALSE, message = FALSE}
#see https://bookdown.org/yihui/rmarkdown-cookbook/write-bib.html
library(knitr)
write_bib(c(.packages()), "./outputs/biocommons_packages.bib")
```
