---
title: "Compute systems at the BioCommons partner infrastructures"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(tidyverse)
library(kableExtra)

QCIF_UQ <- read_tsv("../external/systems.tsv") %>%
  arrange(`System name`) %>%
  filter(grepl("\\|", `Partner organisation`)) %>%
  separate(`Partner organisation`, c("QCIF", "UQ"), sep = " \\| ") %>%
  separate(URL, c("QCIF_url", "UQ_url"), sep = ", ") %>%
  #see post by Hao @ https://stackoverflow.com/a/48512819
  #see post by jrdnmdhl @ https://stackoverflow.com/a/30901774
  #see post by Akrun @ https://stackoverflow.com/a/43696252
  #question url https://stackoverflow.com/questions/43696227/mutate-with-case-when-and-contains
  mutate(
    QCIF = case_when(
      grepl("^https", QCIF_url) ~ paste0("<a href='", QCIF_url, "' target='_blank' rel='noopener noreferrer'>", QCIF, "</a>")),
    UQ = case_when(
      grepl("^https", UQ_url) ~ paste0("<a href='", UQ_url, "' target='_blank' rel='noopener noreferrer'>", UQ, "</a>"))
  ) %>%
  mutate(`Partner organisation` = paste(QCIF, UQ, sep = " | ")) %>%
  select(`Partner organisation`, State, `System name`, Cloud, HPC, System_link)
  
systems <- read_tsv("../external/systems.tsv") %>%
  filter(!grepl("\\|", `Partner organisation`)) %>%
  mutate(
    `Partner organisation` = case_when(
      grepl("^https", URL) ~ paste0("<a href='", URL, "'  target='_blank' rel='noopener noreferrer'>", `Partner organisation`, "</a>"))
    ) %>%
  select(-URL) %>%
  bind_rows(QCIF_UQ) %>% 
  arrange(`System name`) %>%
  mutate(
    `System name` = case_when(
      grepl("^https", System_link) ~ paste0("<a href='", System_link, "'  target='_blank' rel='noopener noreferrer'>", `System name`, "</a>"))
  )

```

Below is a list of the Australian BioCommons infrastructure partners and some of their available compute systems. This list is not intended to be exhaustive, and will be added over time.

-----

-----

# Graphical user interface accessible systems

- [Galaxy Australia](https://usegalaxy.org.au/)
- [SWAN (Rstudio & JupyterLab accessible via AARNet’s CloudStor)](https://support.aarnet.edu.au/hc/en-us/sections/360000129695-CloudStor-SWAN)

-----

-----

# Command-line accessible systems

## High Performance Computing

<font size="2">
```{r}
 systems %>%
  filter(HPC == "Y") %>%
  select(`System name`, `Partner organisation`, State) %>%
  #see https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
  kbl(align = "l", format = "html", escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped"))
```
</font>

-----

-----

## Cloud

<font size="2">
```{r}
systems %>%
  filter(Cloud == "Y") %>%
  select(`System name`, `Partner organisation`, State) %>%
  #see https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
  kbl(align = "l", format = "html", escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped"))
```
</font>

-----

-----

# FAQ: How can I get a HPC allocation??

Allocation of computational resources to individual researchers on partner HPC and cloud infrastructures is through the usual channels offered via each partner (see instructions for each by following these links: [NCI](https://nci.org.au/users/how-access-nci), [Pawsey](https://support.pawsey.org.au/documentation/display/US/Getting+Access), [QCIF](https://www.qcif.edu.au/services/computing/), [ARDC's Nectar Research Cloud](http://cloud.nectar.org.au/start-now/)). The [BioCommons BioCloud](https://www.biocommons.org.au/biocloud) activity is working with these partners to examine ways to make it easier for life science researchers to receive HPC and HTC allocations.

Note that access to computational resources via the [Galaxy Australia](https://usegalaxy.org.au/) hosted web platform is unlimited for Australian researchers thanks to our computational partners (ARDC's Nectar Research Cloud, University of Queensland, QCIF, University of Melbourne and Pawsey) who underpin the Galaxy Australia service.  

-----

-----

```{r echo = FALSE, message = FALSE}
#see https://bookdown.org/yihui/rmarkdown-cookbook/write-bib.html
library(knitr)
write_bib(c(.packages()), "./outputs/compute_systems_packages.bib")
```
